---
title       : Shiny on displaying Investment Portfolio Theory
subtitle    : The power of diversification
author      : Walter Foppen
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Investigate the power of diversification!
 
* a selection of three stocks is available to select your investment portfolio
* each stock has an expected return and an expected volatility
* return and volatility are plotted in a risk-return plot
* based on the inter-correlations, the return and volatility of a select portfolio is calculated
* combining the three assets in a portfolio allows to get solid return with lower risk

--- .class #id 

## Calculation of portfolio return and volatility
 
* Assume that the portfolio distribution is, the expected returns, volatilities and correlations are given by,
```{r}
Share <- c( 0.4, 0.3, 0.3)
Return <- c( 0.03, 0.05, 0.08)
Volatility <- c( 0.12, 0.15, 0.25)
Corr <- matrix( c(1, 0.2, 0.15, 0.2, 1, 0.25, 0.15, 0.25, 1), nrow=3, ncol =3)
```
 
* Then the return an volatility of the portfolio is calculated by
 
```{r}
PFreturn <- sum(Share * Return)
PFvolatility<-sqrt( Share %*% (Volatility * Corr * Volatility) %*% Share )
c(PFreturn, PFvolatility)
```

--- .class #id 
 
## Displaying the effect of shiny inter-activity
 
The following simple changes display the effect of interactivity of this Shiny App.
 
* Increase or decrease the expect return of stock to move its dot up or down
* Increase or decrease the volatility of a stock to move its dot from left to right
* Change the contribution of a stock in the portfolio to move the portfolio dot
 
The following effect can be witnessed if the correlation between assets are changed.
This assumes that the portfolio consists of more than one stock.
 
* An increase in correlation moves the portfolio to the right, i.e. its standard deviation increases
* A decrease in correlation moves the portfolio to te left, i.e. its standard deviation decreases
 

--- .class #id 
 
## Disclaimer
 
* This model assumes investment risk is fully cover by a stock’s volatility
* The model assumes a multivariate normal distribution to determine the portfolios risk
* The model is set up with fictual stocks
* Any investment decision based on the model is for user’s own risk!
